---
title: "DTA_L4_GIT"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
author: Joy Hsu
date: 2018-09-11
---
This R markdown will be used to learn GIT. Markdown copied from L3. Writing with Data.

* Generally, render RMD to HTML document
* name r chunks with something useful

```{r chunk_tidyverse, include = FALSE}
library(tidyverse)
```

#Section 0 - YAML and output formats

* The YAML header controls the global features of the document. Always include author and date
* you can modify the output format with subfields

```{r, eval=FALSE}
#add table of contents to the output
output:
  html_document:
    toc: true
    toc_float: true
#hide all the code in the document until the reader clicks to show it
output:
  html_document:
    code_folding: hide
#different types of outputs:
output:
  pdf_document: default
  word_document: defaults
  github_document
```

#Section 1 - Formatting

* Here's a **code chunk** that samples from a _normal distribution_:

```{r example, collapse=TRUE}
#sample from normal distribution
samp = rnorm(100)

#length of sample
length(samp)
```

#Section 2 - Inline Code & Text

Execute Inline code: `r `
Write inline code: ` `

I can take the mean of the sample, too! The mean is `r mean(samp)`. Nonexecuted code `mean(samp)`.

#Section 3 - Customize Chunk

* `eval = FALSE`: code will be displayed but not executed; results are not included.
* `echo = FALSE`: code will be executed but not displayed; results are included.
* `include = FALSE`: code will be executed but not displayed; results are not included.
* `message = FALSE` and warning = FALSE: prevents messages and warnings from being displayed.
* `results = hide` and fig.show = hide: prevents results and figures from being shown, respectively.
* `collapse = TRUE`: output will be collapsed into a single block at shown at the end of the chunk.
* `error`: errors in code will stop rendering when FALSE; errors in code will be printed in the doc when TRUE. The default is FALSE and you should almost never change it.

#Section 4 - Learning Assessments

1.  The chunk below creates a dataframe containing a sample of size 500 from a normally distributed RV and the absolute value of each element in the sample. A histogram is generated for the absolute values. Note, code can be hidden with `echo=FALSE`.

```{r learning_assessment, collapse=TRUE, message=FALSE}
#create a variable containing random sample size 500
set.seed(1)
x = rnorm(500, 0, 10)

#compute absolute value of each element
x_abs = abs(x)

#produce histogram. 
x_df = tibble(x, x_abs)
ggplot(x_df, aes(x = x_abs), colour = "blue") + geom_histogram()

#Add an inline summary giving the median value rounded to two decimal places.
```

The median of the variable containing absolute values is `r median(x_abs)`

Median round to two digits is `r round(median(x_abs), digits = 2)`

2.  Learning Assessment 2. The chunk below creates a tibble data frame and generates variables directly in the df. Two `geom_point` layer spots.

```{r learning_assessment2, collapse=TRUE}
#tibble - bind vectors into data frame
log_df = tibble(
  samp = rnorm(100, 0, 5),
  log_samp = log(abs(samp))
)

#create plot using variables 
ggplot(log_df, aes(x = samp, y = log_samp)) + 
  geom_point(colour = "black", size = 4.5) +
  geom_point(aes(colour = "blue"))
```

3.  Learning Assessment 3. The chunk below creates a bullet list given the mean, median, and standard deviation of the original random sample.

* The mean of RV is `r mean(samp)`
* The median of RV is `r median(samp)`
* The standard deviation of RV is `r sd(samp)`

#Section 5 - Text Formatting

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------
# 1st Level Header
## 2nd Level Header
### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.

1.  Test

Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell