---
title: "DTA_L3_Writing with Data"
output: html_document
author: Joy Hsu
date: 2018-09-11
---
I'm an R Markdown document! 
*Generally, render to HTML document

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

-Inside section, indicates R code

```{r sample_chunk, eval = TRUE, echo = FALSE}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.
*backtick embeds code in the text 

```{r}

```

```{r}

```

# Section 3 - Learning Assessment
1. Need to indicate library packages to knit. Reproducibility.
1. To load packages, but not display code, use echo
```{r}
library(tidyverse)
```

```{r learning assessment}

norm_samp = rnorm(100, 0, 5)
mean(norm_samp)

log_norm_samp = log(abs(norm_samp))

la_df = tibble(norm_samp, log_norm_samp)
ggplot(la_df, aes(x = norm_samp, y = log_norm_samp)) + geom_point(colour = "black", size = 4.5) + geom_point(aes(colour = "grey90"))
```

1. geom_histogram() - another visualization in ggplot

# Section 4 - Text Formatting

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.

1.  Test

Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell